%This is an example of a reference. \cite[chapter 5.1,p~65]{testRef} 
%\\\\
%This is a new reference, on a new row! \cite{OwenPSP}

%\subsection{Subsection Example 1} % (fold)
%\label{sub:subsection_example_1}
%	Here is an example of a subsection format (check introduction.tex)
% subsection subsection_example_1 (end)

%\subsection{Subsection Example 2} % (fold)
%\label{sub:subsection_example_2}
%	\input{introduction/subsectionExample}
% subsection subsection_example_2 (end)

Today we are offered a vast selection of home security systems. These systems are used to protect and monitor our homes. With this technology, we can feel safe and protected. These alarm systems can however be quite expensive and require difficult installations. With prices that ranges up to 1000\$ \cite{safewise}, often with monthly subscriptions as well, they are not available for everyone. This is a potential problem as every home owner lives with the risk of break-ins. 
 In this project, we propose and implement a cheaper DIY solution to the home security system.

Our proposed solution uses several Zolertia Z1 \cite{z1} micro controllers implemented as wireless sensor nodes to detect different events transpiring. The logged events are saved on a database which can be accessed via a mobile application for easy monitoring. To help with the implementation the real-time operating system Contiki \cite{contiki} is used to program the Z1-nodes. This sensor network could easily be expanded with more nodes and sensors, if the need arises. These expansions would not require any modification to the system to be included in the network, making them easy to integrate.

  

